---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sf2010r

<!-- badges: start -->
<!-- badges: end -->

The goal of sf2010r is to read StanForD2010 forest machine reports and parse these to data structures suitable for R.
Currently the package provide functions to read .hpr and .mom files. The functions have been tested only for a few example files of each category. If they fail please send me an demail to beh at nibio.no, and please attach the file to parse. 

## Installation

You can install the development version of sf2010r from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hbelbo/sf2010r")
```

## Example
This is a basic example which shows you how to use:

```{r example}
library(sf2010r)
## basic example code



# Get a list of the first three example files provided in the packagehttps://mail.google.com/mail/u/0/#search/miele/FMfcgxmSdZDpKdbMpMbsxFtgFmrxNdfh?projector=1&messagePartId=0.1
sf2010r_example()[1:3]
# Get a list of the "hpr" example files provided in the package
hprfiles <- sf2010r_example(fileending = "hpr")
hprtest1 <- hprdata(hprfiles[1])




```



Remenber to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` 


